---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ReQual

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/RE-QDA/requal/workflows/R-CMD-check/badge.svg)](https://github.com/RE-QDA/requal/actions)
<!-- badges: end -->

The goal of `requal` is to provide reproducibility support for qualitative coding.  

⚠️__The package is in development and in experimental stage.__⚠️

## Installation

### Prerequisites

To use `requal`, you need to have the [R language](https://www.r-project.org) installed and running on your machine. You can download and install R from [here](https://cloud.r-project.org)). You will also need a web browser with JavaScript support (i.e. any of the standard issue browsers like Firefox, Chrome, or Safari).

### Package 

You can install the development version of `requal` from [GitHub](https://github.com/) by running this code in R:

```
install.packages("devtools")
devtools::install_github("RE-QDA/requal")
```

## Usage

The `requal` app can be launched from the R console with the following command:

```{r example, eval=FALSE}
requal::run_app(options = list("launch.browser"))
```

On the first launch of the app, use the "Create" menu to set up a new project by providing a name a selecting a folder for your project. The app will create an SQLite database file with the `.requal` extension and start up the project.

`requal` is a `shiny` application that runs in your browser and provides basic functionality for annotating documents in plain text with user-defined codes. The annotated text segments can be filtered and exported. More functions are coming up.

## Acknowledgement

The application development has been supported by The Technology Agency of the Czech Republic, project n. TL05000054.
