---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# requal

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/RE-QDA/requal/workflows/R-CMD-check/badge.svg)](https://github.com/RE-QDA/requal/actions)
<!-- badges: end -->

The goal of `requal` is to provide reproducibility support for qualitative coding.  

## Installation

### Prerequisites

To use `requal`, you need to have the [R language](https://www.r-project.org) installed and running on your machine. You can download and install R from [here](https://cloud.r-project.org)). You will also need a web browser with JavaScript support (i.e. any of the standard issue browsers like Firefox, Chrome, or Safari).

### Package 

You can install the development version of `requal` from [GitHub](https://github.com/) by following these steps (assuming you have R installed on your machine :

1. download the current release of `requal`` from [Releases](https://github.com/RE-QDA/requal/releases).
2. install `remotes` package by running `install.packages("remotes")` command in R console.
3. install `requal` package by running `remotes::install_local(file.choose())` and selecting the downloaded `requal` release file on your hard-drive. 

## Usage

The `requal` `shiny` application can be launched with the following command:

```{r example, eval=FALSE}
requal::run_app(options = list("launch.browser"))
```

The application runs in your browser and provides basic functionality for annotating texts with codes. The annotated text segments can be filtered and exported. More functions are coming up.

## Acknowledgement

The application development has been supported by The Technology Agency of the Czech Republic, project n. TL05000054.
